### 2016-08-16 R/ITHIM.Rmd
Investigated whether Speed is logNormal

Dwalk <- data.frame(Hours = walkHours, Miles = walkMiles, mode = "walk")
Dcycle <- data.frame(Hours = cycleHours, Miles = cycleMiles, mode = "cycle")
D <- rbind(Dwalk,Dcycle)

@@

g <- ggplot(D, aes(Hours, Miles, colour = mode)) + geom_point()
g <- g + geom_abline(aes(slope = speed, intercept = intercept, colour = mode), Dspeed) + facet_grid(. ~ mode)
g + scale_y_log10() + scale_x_log10() + theme_bw()
```

>>>>

Dwalk <- data.frame(Hours = walkHours, Miles = walkMiles, Speed = walkMiles/walkHours, mode = "walk")
Dcycle <- data.frame(Hours = cycleHours, Miles = cycleMiles, Speed = cycleMiles/cycleHours, mode = "cycle")
D <- rbind(Dwalk,Dcycle)

@@

g <- ggplot(D, aes(Hours, Miles, colour = mode)) + geom_point()
g <- g + geom_abline(aes(slope = speed, intercept = intercept, colour = mode), Dspeed) + facet_grid(. ~ mode)
g + scale_y_log10() + scale_x_log10() + theme_bw()

g <- ggplot(D, aes(log10(Speed), ..density.., fill = mode)) + geom_histogram(bins = 25) + facet_grid(. ~ mode)
g
